\documentclass[char]{Kos}
\begin{document}
\name{\cArmsDealer{}}

	War is good for business. That’s what everyone says, at least. And you suspect that the old adage might well be true. But you’d like to put it more precisely: war is good for your business. That is to say, your business happens to be the sale of new and deadly weapons to the highest bidder. And if you want to get Etruria and Scythia to pay a premium for your newest innovations – well, then war could be quite profitable indeed. Now you just need to make sure a devastating conflict ensues – and since you’ve been invited to the royal wedding, alongside the rulers and heirs of both factions, it seems like an excellent time to manipulate the situation and make sure things go your way.

	You’ve been attached to the royal court of Scythia for years now, trading military secrets with incautious generals and making sure the royal guard stays well-supplied and heavily armed. During this time, you’ve managed to develop a contact at the very highest levels of the Scythian government: you’ve cultivated quite a friendship with no less than Queen Meizon herself. You first bonded over your shared hatred for Etruria – yours has been feigned from a young age, ever since you realized that nothing sells weapons more convincingly than patriotism. But you’ll never share that particular revelation with Meizon, since her loathing for that rival nation appears to be frighteningly, sometimes terrifyingly, real.

	Thankfully, you’ve got evidence to back up your claims. Years back, when the Etrurians razed the border town of Achillea, three of your cousins were killed by King Hiems’s troops. They were second cousins by marriage, and you never really liked them anyways, but that’s not the point – and you certainly don’t mention that last part when you’re speaking to the Queen. Instead, you let a couple of tears fall – a wonderful talent, the ability to cry at the drop of a hat – and Meizon’s ready to put reason aside and let her wrath take over.

	Meizon, you suppose, has reason enough to despise Etruria. First they killed her childhood friend when they burned down Achillea, then they took her own daughter from her in the night. She’s lost a lot. But try as you might, it’s hard for you to imagine the white-hot emotions coursing through her veins. Profit and opportunity speak to you most dearly, not pathetic sentiment – but if you can use the Queen’s emotions to sway her towards war, then you’ve no compunctions about doing so.

	Unfortunately, not everyone agrees with you on that particular point. Also attending the wedding is the Etrurian merchant Paldeen, a purveyor of luxury goods and a pacifistic coward. Not that Paldeen’s got any more moral compunctions than you do – as a matter of fact, he’s a vile and avaricious termite of a man. He craves profit even more shamelessly than you – and he’s not got an honest bone in his body. He’s a conniver, a deceiver, a forger, a manipulative bastard who will stop at nothing to quash the fledgling conflict between the Sabine factions and peddle his posh snake-oil trinkets to the rich and stupid nobles of both nations. You’ve encountered the man too many times before. Even worse, he’s gotten the better of you as often as not. This is embarrassing, it’s humiliating, and you’ll never admit it to your customers. It’s surprisingly difficult for you to damage his credibility – you’ve tried accusing him of being a dirty money-grubbing piece of slime who cares about nothing but profit, but he always manages to twist your words around and fire them back at you. No good, no good at all.

	This time, though, Paldeen’s overstepped his bounds, and if you play your cards right, you might well be able to destroy his reputation permanently. The fool’s been bragging to anyone who will listen that he’s come across an ancient relic – the legendary Diadem of Queen Smaragdos. Thankfully, you’ve done your history research. You’ve always loved history, ever since you realized that no one knows more about starting wars than the historians. Anyways, every source you’ve read about the Diadem mentions that the artifact was lost on the island of Cos, a site that Paldeen’s never visited – so it’s inconceivable that he could possess it. Therefore, you’ve concluded, Paldeen’s version must be a fake. 

	The tricky part will be proving it. Paldeen’s not only a nefarious forger, but also a talented one – and you’ve no doubt that he’s imitated the Diadem as closely as he can. So there’s only one way to show the assembled royals that Paldeen’s a liar, and his wares are spurious: dig up the real Diadem from its long-forgotten hiding-place on Cos and show it to the crowd. Thankfully, you’ve got some leads in this regard – your preliminary research suggests that it disappeared [insert information from wherever the initial part of the treasure-hunt points her].

	You’ve also got no love lost for Hiems, Etruria’s cruel genius of a king. You know he’s brilliantly intelligent, but also suspect that he may have intercepted one of your recent arms shipments containing a powerful but unpredictable new explosive – the bireme conveying it disappeared without a trace several weeks prior. You think Etruria’s planning to use the weapon to attack Scythia and catch Cryseon by surprise. Now, that’s not necessarily a bad thing

Wants to get poison samples from the Blackguards (legends substantiated)

Fresi has had previous contacts with (Assyrian) blackguards


\end{document}
