\documentclass[char]{Kos}
\begin{document}
\name{\cAssassin{}}

	No wise king travels unattended, and Hiems Coronus is no exception. At the subtlest gesture – a shrug, a nod, the twitch of a finger – a wordless, dutiful servant appears behind him, ready and willing to serve. It is for this purpose that the Etruscan court keeps a highly trained and disciplined staff, ready and willing to supply whatever the king should require. Though the royal wedding takes place on the remote isle of Cos, he has chosen you, his favorite attendant, to accompany him.

	But you were trained to be far more than a mere attendant. That’s nothing more than a cover story, meticulously rehearsed and years in the making. You are one of the most proficient of Etruria’s nefarious and secretive order of Blackguards, and King Hiems’ most reliable agent. In all of Etruria, you answer to only two people: the White Rose, the elusive commander of the Blackguards, and the King himself. To maintain the utmost degree of secrecy, even the King has no idea who you really are: he sends his commands to the White Rose via a hidden communications device, and the White Rose relays those orders to you.

	Until recently, you didn’t even answer to the two of them. You were happily retired, ready to while out the rest of your days at a Mediterranean estate. But you kept up with Etruria’s political affairs, just to while away the time – and, let’s face it, the next generation of Blackguards has been making a gods-awful mess of things. After reading about debacle after debacle, you lost all faith in those incompetents. So when the White Rose offered you an opportunity to accompany Hiems’ retinue to the wedding and defend him against Scythian treachery, you knew you had to accept. If anyone else took the assignment, Hiems would be, quite frankly, as good as dead. 

	Not that you’ve any love for Hiems himself. You remember his father, Hyperion, with nothing but bitterness, and long for the good old days when women of pure Etrurian blood sat upon the throne. But it’s the worst form of dishonor for a Blackguard to act against their rightful ruler, no matter what their personal feelings might be. So you’ll swallow your pride, and provide a shining example to the newer Blackguards of what it means to be a true professional. Nevertheless, rumor has it that despite the best efforts of the Coronus dynasty, at least one full-blooded Etrurian royal survived the coup. 

	Spy, courier, assassin

	Purists (sort of Omerta among Blackguards)

	No love lost for Hiems, or for the Coroni in general - supporter of Etruria and suspects that someone survived.
	
	Still, better than the Assyrian blackguards (in disarray) or the Scythian blackguards (dead)

	Ordered to accompany Hiems’ retinue and protect him against potential Scythian treachery

	Received recent orders to kill first Salo, then Felix. Seems a bit strange that Hiems would want both brothers dead, but who are you to gainsay a king? Looking not just for a kill, but for a ‘clean’ kill. No suspicion. No kills unless commanded or absolutely necessary.

	Care about the long game - rebuilding the power and reputation of the Blackguards

	Looking to meet up with another Blackguard, from Assyria, who’s contacted her in the past, to (at most) cooperate or (at least) keep an eye on him. (sign of the White Rose)

	As a Blackguard, you also harbor no love for Scythia’s Soulblades and want to do whatever you can to get under their skin and sabotage their magic



\end{document}
