\documentclass[char]{Kos}
\begin{document}
\name{\cButler{}}

Born November 7, in the year 276.

Nobody lives happily ever after, but I swear I’ll still try.

I grew up cursed by my own talents. My father was Memnon, one of the celebrated Scythian Soulblades, but he proclaimed at my birth that I had more potential than any other mage, ever. He therefore inducted me into the horrors of life and death magic when I was still a babe, and my earliest memories were filled with the rattling of bells, the murmuring of malevolent ghosts, with black zigzags that stuck to me like bandages on a mummy. The black magic nearly drove me insane, and I fled when I was just nine, running for miles to non-magical relatives on my mother’s side. I never had to go back to Scythia's Soulblade Quarter, because it was raided soon afterwards. It turned out the Soulblades had been breaking the law with their black magic, for the Scythians allowed them to practice healing magic and nothing else. Father was jailed for life, and I never saw him again.

Thus, a new chapter began. I dropped out of school at fifteen-- though I still read often and am hardly ignorant-- with hopes of working in the palace. I was personally interviewed by\cQueenTwo{\Monarch} \cQueenTwo{\nickname}, and \cQueenTwo{\they} asked whether I had indeed abandoned the Soulblades, whom \cQueenTwo{\they} openly opposes; I promised I had left them entirely, and I suspect \cQueenTwo{\they} verified my answer with royal divination magic. Soon afterwards, I began as a server in the dining halls and rose through the ranks, performing my duties as diligently and elegantly as possible. I am quite loyal to Scythia and glad to serve it, and the orderly nature of palace life was a comfort after my chaotic childhood.

But a few years ago, my world was thrown back into disarray. There was a ball at the Scythian palace, in honor of the crown \cBride{\prince} \cBride{\nickname}, who had recently returned from law school in Assyria. Before, I thought of \cBride{\them} as a coltish adolescent, but I now saw an angel in white and gold robes, radiant with some inner joy. Enthralled, I continued to watch \cBride{\them}. At first, I could do nothing but admire \cBride{\them}, like a fine statue, for \cBride{\they} seemed too perfect to be real. But I slowly discerned something underneath the brilliance-- anxiety, and a depth of pain-- and I fell in love. 

Loving \cBride{\them} hurts, though. The more I watched \cBride{\them}, the more I grieved, for \cBride{\they} clearly struggles with great burdens. \cBride{\Their} \cFugitive{\sibling} disappeared, yes, but I can’t help feeling that \cBride{\nickname}’s suffering from fresher pain as well. Soon afterwards, I was promoted to steward, the top position in the servants’ hierarchy, so I had the freedom to move throughout the whole palace at all hours and observe \cBride{\them} more closely. What I found stunned me-- \cBride{\they} was an alcoholic.

I immediately knew I had to help \cBride{\them}. And so, after so many years of shunning Soulbladery, I returned to magic-- healing magic, specifically. Though the Soulblades had never found a cure for alcoholism, I threw my efforts into the search and, after a few months of experimentation, concocted a partial remedy; while I could not guarantee that \cBride{\they} would be healed, I would at least increase \cBride{\their} chances. So I slipped the cure into \cBride{\their} soup at dinner, and, from the next day on, \cBride{\they} ceased drinking. I rejoiced, thrilled to have helped \cBride{\them}.

Then, six months ago, I learned that \cKingOne{\Monarch} \cKingOne{\nickname} of Etruria and \cKingTwo{\Monarch} \cKingTwo{\nickname} of Scythia had arranged a marriage between \cBride{\nickname} and the Etruscan crown \cGroom{\prince} \cGroom{\nickname}, in order to fulfill an ancient prophecy and prevent civil war. Immediately, I could sense \cBride{\nickname}’s mental state deteriorating, though \cBride{\they} hid the distress well from the rest of the world. And so, I began to dread this wedding, partially out of envy, more because of my concern for \cBride{\them}.

I have only a few ways to help \cBride{\them} now. I fear \cBride{\they} will turn back to alcohol, and so I must remove undue temptation from \cBride{\their} path. Upper-class weddings always come paired with loathsome side parties hidden in the corners of the venue, where noblemen lose themselves to debauchery and lose quite a bit of money gambling in the process. While I have always found these gatherings distasteful-- it pains me to see noblemen, normally so elegant and composed, debase themselves-- I haven’t stepped in. This time, though, I must be a spoilsport, for I won’t let their carrying-on risk \cBride{\nickname}’s sobriety. In the case that I fail, I have brought in the ingredients for the remedy I slipped \cBride{\them} last time, but, as it is not a guaranteed cure, I would prefer to avoid a relapse in the first place.

These are small ways to help \cBride{\nickname}, and I worry that I cannot even do this much, once \cBride{\they} is married and moves to Etruria with \cGroom{\nickname}, who is a few years older. Once \cBride{\they} goes, I know I will never be happy again. Thus, for months now, I have dreamed of running away with \cBride{\nickname} and eloping. I haven’t gone through with this foolish notion-- I suspect \cBride{\their} disappearance would hinder Scythian political affairs, and, more importantly, I don’t even know how \cBride{\nickname} feels about me. But if this wedding threatens \cBride{\their} health and sanity too greatly, I will confess my feelings for \cBride{\them}. I’ll ask \cBride{\them} to break off \cBride{\their} engagement with \cGroom{\nickname} and perhaps consider me instead, though I am naught but a lowly steward. Should \cBride{\they} prove agreeable, we should depart from the wedding as soon as possible to avoid a stampede by various relatives and spurned in-laws-to-be, so I’ll stay on the lookout for boats or other mechanisms by which to leave the island.

I wonder what other surprises are lurking on this island. While I’ve never heard of Cos, I remember the name “Acheron”-- the bay where Cos is located-- from those horrific Soulblade chants inflicted on me as a child. The word “ghost” was always close by. Those two words have resurfaced in my dreams, recently, along with strange golden sigils I’ve never seen before. They’ve made me curious, and I intend to investigate any signs of the paranormal.

Moreover, I’ve recently received a message from the Soulblades, sent to anyone who’s ever studied with them. It warns that the Blackguards, their ancient, anti-magic rivals, intend to strike once more. Given that the warning came just before the wedding, the Blackguards-- renowned as skilled assassins-- may be aiming at this wedding, and \cBride{\nickname}’s life might very well be at risk. I want to defend \cBride{\them}, but I, too, am likely a target. Thus, I should engage in magical activities quietly and try to avoid the Blackguards’ notice, for even ex-Soulblades may incur their wrath.

If all goes fairly well, \cBride{\nickname} and \cGroom{\nickname} shall be married tomorrow. If all goes perfectly, \cBride{\nickname} will be married, and to me. But should the Blackguards strike \cBride{\them} down, we may still have our “happy ever after,” if not in this world, then in the next . . .


\end{document}
