\documentclass[char]{Kos}
\begin{document}
\name{\cKingTwo{}}

	The legends tell of an ancient Scythian king named Damocles the Just who commanded his smiths to fashion him a sword keener than a lion’s fangs. When it was completed, his advisers feared that he would lash out against his neighbors, fueled by mad dreams of conquest. Instead, he stood before them, unspooled a single silken thread, and wound it about the hilt. The sword would not be used for war, he decreed. Instead, it would hang above his throne until the day he died. Whenever he or his descendants gazed up at the hanging blade, he hoped that they would be reminded of everything that is at stake whenever a ruler acts – that even a single reckless misstep or careless blunder could bring bloodshed and disaster crashing down upon the kingdom. A ruler should live out every day as if his life, his people, and his domain hang in the balance – and he should do everything in his power to preserve them.

	You learned this lesson from your grandfather, who learned it from his grandfather, who, the stories say, learned it from King Damocles himself. For too long you thought it was nothing but a foolish children’s story, just more outdated prattle about “duty” and “responsibility.” And then your grandfather died, and then your father – and then it came time for you, not Cryseon the boy but Cryseon the king, to take the throne of Scythia yourself. You remember all too well the first moment you looked up and saw that lethal sword, still hanging suspended above you by a single timeworn thread. The gilded marble of your throne suddenly felt cold as death beneath you. And you realized the crushing weight of the power you now wielded.

	You have borne that weight for more than thirty years now, borne it gravely and with pride. And the people of Scythia have always loved you for it. Your citizens trust, admire, respect, and cherish you – and you have always strived in turn to keep them safe and content. You were married with great aplomb to an old acquaintance, Meizon, and bore two children with her, your beloved daughters Thoesi and Eidola. You were happy. And, more importantly, you kept the great nation of Scythia stable and peaceful for years.

	Then, one day, something unexpected happened. You found yourself falling in love for the first time in your long life. A minor noblewoman in the royal court, Musa, caught your eye, captivating you with her mischievous smile and her incredible intellect. Musa was never the most beautiful or most proper of Meizon’s ladies-in-waiting, but she was undeniably the most fascinating. An irrepressible practical joker, she loved to get the better of her stuffy colleagues, engaging in juvenile – but brilliant – pranks at their expense. You loved nothing more than hearing the clarion of her laughter echoing through the halls.

	Whenever Assyria sent emissaries to your court, geniuses and academics all, Musa loved to match wits with their most renowned archaeologists and poets, whiling away her spare time in games of Senet. She almost always won. A venerable Assyrian scholar, watching her play, had once pulled Cryseon aside with words of praise, remarking, “If she had only been born in Assyria, my lord, she would be one of the greatest scholars our nation has ever seen.”

	You kept yourself from acting on your affections – you were a king, after all, and a king never imposes himself upon his subjects – but you always wondered what might have happened if you had expressed your feelings. Then, one cold autumn night, when Meizon was off in Assyria on a diplomatic mission, there came a shy knock on the door of your bedchamber. It was Musa. You couldn’t keep from laughing, warm and genuine, more than you had in years. Then she joined in, warming the cold marble stones of the palace with her amusement. It was the first night you shared with her, but not the last. You wished sometimes, in your most tender moments, that you could abandon the charade, abandon even the throne, marry Musa, and retire to a distant home. But the kingship – your duty to Scythia – weighed on your shoulders more heavily even than love. And so your moments with Musa were limited to those nights, too few and far between, when Meizon was away and the palace was quiet.

	Then you overheard the high priest of the Soulblades, a pompous but well-meaning man named Epidotis, mention that one of Meizon’s attendants was with child. The woman he spoke of was Musa. Epidotis neither knew nor cared who the child’s father was, but you did. If you were revealed as the father, your reputation as a just and moral king would collapse in an instant, and – you feared – Scythia’s stability would crumble with it. You knew the choice you had to make. So you saw to it that Musa was married off to another minor noble, Polutrupon, and sent off to a remote town on the Etrurian border, the prosperous hamlet of Achillea. Meizon, an old friend of her husband, told you when their first child was born, a son named Maxenes. No one – perhaps not even Polutrupon – ever suspected that Max had royal blood.

	Your feelings for Musa were soon the least of your worries. The peace between Etruria and Scythia – a peace that you had worked for years to maintain – was beginning to crumble. The nations were still far from all-out war, but a series of border skirmishes and assassinations began to plague your citizens. One of the first towns to be destroyed was Achillea. Etrurian raiders burned it to the ground one fateful autumn day, leaving Musa and her husband dead in the wreckage. Then Queen Meizon ordered Scythia’s own troops to retaliate, in an attack that not only destroyed a border settlement but claimed the life of the Etrurian queen, Cerintha. Only weeks later, your eldest daughter, Thoesi, vanished, kidnapped and slain by Etruria’s nefarious Blackguards despite the best efforts of the Soulblades. So much death, hanging above your head. Meizon, if anything, seemed even more scarred by these tragedies than you: once a wise and gentle woman, she appeared to go half-mad with grief and rage, retiring to her quarters and admitting no one for several weeks before emerging and swearing revenge against Etruria. To see such bloodlust, such vengeance, in the heart of someone once ruled by reason and compassion, has shaken you deeply.

	One good thing did emerge from the rubble. Despite the devastation wrought on Achillea, Musa’s son Maxenes somehow managed to survive. Desperate to see your son, you took advantage of Meizon’s friendship with Musa’s dead husband and convinced her to adopt Max as your own child. On other matters, however, you disagreed. After the destruction of Achillea and your daughter’s death, Meizon wanted war – wanted to crush the upstart Etruscans at any cost. But you would have none of it – you never wanted so much blood on your hands. Broken by sorrow, torn between your duty to Scythia and your duty to your wife and daughter, you found solace in glass after glass of wine, until strong drink and stupor were the only things that could truly dull your pain. 

	For his part, Max proved to be both a blessing and a curse. Like his mother, he proved both brilliant and mischievous, prone to elaborate practical jokes. Openly, you claimed to detest his talent for chaos – inwardly, however, he reminded you all too much of Musa. So you distanced yourself from him, lest Meizon realize that you had once loved his mother. When you sent Max off to school in Assyria, it was a weight lifted from your shoulders. His professors always spoke admiringly of him, and one, an archaeologist named Izdubar, once remarked that Max was one of the greatest scholars Assyria had ever seen.

	Sadly, Max seemed prone to bad habits of his own. The royal court of Scythia had seen fit to provide him with a stipend while he studied in Assyria, to provide for his basic well-being. A few weeks ago, you decided to take a look at the receipts Max was sending back – and what you saw surprised and dismayed you. According to the documents accumulated by the court, one of two things was true. Either Max was embezzling money from the crown for his own purposes, a blatant violation of Scythian law that you could not condone, or he was (as the receipts suggested) squandering almost all of his money on strong drink and lavish parties. You’re not sure which is worse. Seeing your son indicted for his criminal behavior would be shameful – but watching him mirror your own descent into alcoholism would be heartbreaking.

	But perhaps you have a chance to make things right. Now, with King Hiems’ unexpected offer to seal a peace by marrying his son Felix to your remaining daughter Eidola, you’ve been given a chance to make things right, to salvage the decaying relationship between the two nations. You’d like nothing more. But no negotiation with Etruria is ever as simple as it seems, and things have only grown more complex once Hiems ascended to the throne. As cunning as he is cruel, you suspect that he’d like nothing more than to crush Scythia beneath the heel of his boot – and you cannot allow him to catch you off guard. 

	The Scythian court is already far more vulnerable than you would like. Despite your best efforts to fill it only with trustworthy and reliable advisors, recent events have suggested that an Etrurian spy has managed to infiltrate your retinue: it seems that Etruria’s one step ahead of you at every turn. Every time you contemplate waging war against Etruria with a spy in your midst, your heart becomes ice and your ribcage turns to ash. Unless you can root out the spy and stop their nefarious betrayal, any war with Etruria will cost too many lives, too much defeat, to even be an option. 

	Thankfully, you already have some idea who the culprit might be. Your daughter Eidola recently told you that she saw your chief attendant, a soft-spoken but reliable man named Prymnesios, trying to slip an unidentified substance into her drink. When you heard of this affront, you had half a mind to execute the man on the spot, but decided it would be better still to figure out just how he’s connected to King Hiems – the better to spot the next spy when he shows up on your doorstep, or even to feed Hiems false information. Or perhaps Prymnesios is innocent, one of those young fools preoccupied with love potions and royal romances, with no knowledge of courtly intrigue. Another potential suspect is the most recent member of your retinue, a fortuneteller named Delia with a suspiciously nondescript background. But you have to know for sure: as long as the leak remains, the lives of your fellow Scythians are in grave danger.

	If worst comes to worst, the power to launch a pre-emptive strike against Hiems rests in your hands. You will do everything you possibly can to prevent this outcome – so much senseless hate, so much bloodshed – but if Hiems’ machinations prove too dire, then rallying Scythia’s forces before it is too late may well be your only option. To put it bluntly, you suspect that he’s only indulging in this wedding ritual at all to lull you into a false sense of security as he prepares an attack on all fronts. To prepare for this eventuality, your nation’s greatest artificers have crafted an arcane communications device with which you might inform your generals of your decision. If you decline to use the communicator, nothing will change: no armies marshaled, no battle plans drafted, no swords sharpened or armor girded. If, however, relations between the two factions should deteriorate, you have two further options. If tensions escalate, but a chance for reconciliation remains, you have the power to increase Scythia’s border defenses, preparing for the worst (and risking further escalation) without acting aggressively. But if all else fails, one option still remains: the metaphorical sword of war yet hangs above your head, and all you need to do is sever one thread to unleash it.

Doesn’t want to give up his daughter to Etruria, but would rather marry Eidola off than plunge the nation into all-out war

	You hope against hope that the wedding will not come to such a disastrous end, however. A large part of this result, you know, depends on you – so long as you can find the spy in your own retinue, remain aware of Hiems’ attempts to manipulate Scythia, and keep your wits about you, you may well be able to forestall any Etrurian treachery and keep the peace between the kingdoms. But with war looming, the burden of rulership is heavier than ever upon your shoulders, and you can scarcely endure it unaided. Loath as you are to acknowledge it, the fire of a strong drink will ease your fears, if only for a moment. You need it – gods be cursed, how you wish you didn’t – to keep yourself from breaking down utterly. No one must discover you in a moment of weakness, however, or the people will know how frail and desperate you have become. They must see the strong and noble king you strive to be, not the mortal man you are. 

	What’s more, your wife Meizon, usually a proud ruler, confidant, and mother in her own right, has been strangely pale and reserved of late. 

Look after his wife (who’s seeming a tad pale and out of it of late), find some alcohol


\end{document}
