\documentclass[char]{Kos}
\begin{document}
\name{\cWard{}}

Born January 5, in the year 281.

My hometown, Achillea, had been in Scythia’s possession for decades, though it was only a few miles from the Etruscan border. Etruria decided to burn Achillea down to ground, and they torched the manor of my family, the residing nobles. Being a hyperactive four-year-old at that point, I had run away from naptime and was hiding in the garden when everyone inside went up in smoke-- my parents, my sister, the servants, four cats . . . And that, everybody, is why I don’t talk about my childhood much.

Most of the kids who survived the fire ended up in orphanages or on the streets. I got scooped up and saved by the official palace of Scythia, because I’ve got a speck of royal blood in me and because my dear \cQueenTwo{\Monarch} \cQueenTwo{\nickname} knew my parents way back when. Possessed by a fleeting charitable instinct, the monarchs adopted me, but not really, so now I’m a \cWard{\prince}, but not really, and I’m their kid, but really not.

I lived in the Scythian palace, in a room that was larger than any of the servants’ yet still smaller than the wine cellar. I had a retinue of governesses and tutors, and I find it telling that “retinue” comes from the old word “retinere,” meaning “to hold back.” They seemed like wardens, dedicated mainly to keeping me out of the real royal family’s sight, and they never taught me much of anything besides how to wheedle out of punishment. I never even got the same wardens-- I mean, “tutors” as \cBride{\nickname}, my inhumanly perfect non-\cBride{\sibling} \cBride{\sibling} whom I never saw, even though we supposedly “grew up together.” Everything \cBride{\nickname} had was better-- better rooms, better tutors, better books. I swear \cBride{\they} even had better tantrums.

For a while, we both threw tantrums. My whole family burned to death when I was four. Not long afterwards, \cBride{\their} ten-year-old \cFugitive{\sibling} \cFugitive{\nickname} got abducted from the palace in the middle of the night and executed by Etruscans. We’re both screwed up. Of course, darling \cBride{\nickname} had \cBride{\their} \cKingTwo{\parent} \cKingTwo{\nickname} to run to for comfort, while I settled for chucking books out the windows, being scolded by both teachers and gardeners, and chucking more books. I ended up arrogant while having low self-esteem, spoiled without getting a thing I wanted, a bratty ball of contradictory emotions. 

You think I’m stupid, right? Of course you do, and my younger self would have agreed with you. But after a few years, I decided to laugh instead of crying, and I realized that, if I was going to be asininely rebellious, I should at least direct my asininity into productive outlets. While angelic, flawless \cBride{\nickname} always irritated me the most, \cBride{\their} \cQueenTwo{\parent} \cQueenTwo{\nickname} was my least favorite adult; I could sense \cQueenTwo{\their} loathing every time we met, which was rarely, since \cQueenTwo{\they} kept out of my way and I was forcibly kept out of \cQueenTwo{\theirs}. It was fairly well known that \cQueenTwo{\they} was inexplicably feuding with the Soulblades, Scythia’s highly-respected mages-turned-healers. Naturally, I decided to become a Soulblade, just to see my “\cQueenTwo{\parent}”’s reaction.

\cQueenTwo{\They} was furious. \cQueenTwo{\They} would have likely thrown me out of the line of succession; fortunately, the monarchs had never deigned to put me in, as if I needed more reassurance our “child-parent” relationship was a sham. Lacking that option, \cQueenTwo{\they} threatened to kick me out of the palace, but \cQueenTwo{\their} \cKingTwo{\spouse} decided to pay attention, for once, and put \cKingTwo{\their} foot down. And so, I joined the Soulblades, and the strangest thing happened, something nobody could have predicted. It turned out I was a genius.

For the first time, I escaped regimented palace life, as I spent my days in the Soulblade Quarter. For the first time, I felt free, strangely happy as I studied for the qualification exams. Though I had only a limited background in science or medicine, I learned quickly from the healers there, and I scored perfectly on the exam, as only three other students ever had before. Once I entered into the program, I progressed rapidly, and my mentors called me an “intellectual powerhouse.” This was something of a shock to me, and it would have been to my adopted family, had I told them. But I didn’t tell them, mainly because they never asked.

Soon, it was time for me to follow the typical path of young “royal” adults and head off for school in Assyria. I left off my Soulblade training and switched from medicine to astronomy, just to see if I could get any nerdier, and I settled down in the school-city Nineveh. I aced the introductory classes and found myself in an advanced seminar just as a first-year. Somewhere along the way, I realized Assyria was my own personal paradise. Even with all the exams and problem sets and unpaid internships, life there was infinitely less stressful than back at the palace. I collapsed into an existential-angst-ridden identity crisis for a full hour. Then, I decided I was done being Scythian.

Ideally, I’ll spend my future studying in Assyria, then researching in Assyria, then being a seemingly stuffy, secretly awesome professor in Assyria. Unfortunately, as long as I have Scythian citizenship, I am legally bound to return to Scythia once every year, and I also can’t hold a decently paying job anywhere else. Thus, I need to switch my citizenship as soon as humanly possible. I also need money to then support myself until I can get work as a researcher or teacher.

As far as switching citizenship goes, I’m afraid I procrastinated until finals were over. But now I finally did my legal research and purchased the necessary magical form from a low-level enchanter just before leaving for Cos. I need two signatures to complete it-- one from a Scythian monarch, one from an Assyrian who will “sponsor” me. Both have to sign off within the same day. The form, which is currently red, will turn green once it's been properly completed, and then I can file it once I get back to Nineveh. To make things a bit more complicated, both signatories must verify that I'm virtuous and highly productive. \cQueenTwo{\Monarch} \cQueenTwo{\nickname} probably wouldn't sign it even under pain of death, so I'll be relying on \cKingTwo{\nickname} instead.

In addition to documentation, I need the money to survive until I find work. So far, I've saved up about 250 gold coins from two different sources. While I remain a proper Scythian \cWard{\prince}, I can request up to 500 gold coins a year from the Scythian treasury to pay “personal expenses.” I requested all 500 last year, claiming I needed some of it for tuition and housing and the rest for parties (read: liquor), and they actually approved the request, though I shouldn’t count on that happening again. Now, I didn’t spend (most of) it on liquor; I put it in a bank like a sensible person, but that’s technically embezzlement, so . . . 

Though I didn’t throw parties myself, I certainly had my share of college “fun.” \cPoet{\Prince} \cPoet{\name}, the younger child of Etruria’s \cKingOne{\Monarch} \cKingOne{\name}, is studying poetry in Nineveh. Now, \cPoet{\they} throws the most obnoxious bashes imaginable every weekend. The first time I showed up, \cPoet{\they} didn’t throw me out for being a so-called Scythian \cWard{\prince}, and that was the start of a glorious relationship. I drink \cPoet{\their} wine and beat all \cPoet{\their} other guests at Bluffmaster and say all manner of roguishly cynical things. \cPoet{\They} laughs and keeps letting me in. And cynicism’s quite profitable-- though Assyrians don’t play for particularly high stakes, my Bluffmaster winnings have piled up nicely.

Still, the winnings and “party money” add up to no more than 250 gold coins. Even if I advance through the astronomy curriculum speedily, I won’t be able to land real research jobs for at least two years, and I can’t count on Assyrian Bluffmaster parties to tide me over. Thus, I need at least 1500 gold coins in order to be financially secure, and I don’t intend to give up my Scythian citizenship and stipend otherwise.

Fortunately, \cBride{\nickname}’s getting married to \cPoet{\nickname}’s \cGroom{\sibling} \cGroom{\nickname} today, and I have an excellent chance of completing both my immigration form and my financial goals during the festivities. I will get signatures both from \cKingTwo{\nickname} and one of the Assyrian peacemakers, so I can file the document as soon as I return to Nineveh and never have to visit Scythia again. As far as the money goes, I’ve got several options. As the little siblings of the betrothed, it’s my and \cPoet{\nickname}’s duty to throw the real wedding party, complete with card decks and plenty of drinks. Seeing that most of the guests are tackily rich, the Bluffmaster game here will have higher stakes than anything back in Assyria, so I can make a tidy sum.

Of course, there’ll be plenty of money thrown around even outside the game. Both of the representatives of the commoners will be bringing elaborate gifts, and I heard at one of \cPoet{\nickname}’s parties that \cMerchant{\nickname}, the Etruscan representative, has something special in mind, with “special” likely meaning “expensive.” All those precious goods just lying around . . . Suddenly, it doesn’t seem so hard to pick up 1250 gold coins, does it?

There’ll be a few other points of interest at this wedding. With any luck, it’s my last time seeing \cBride{\nickname}, which means it’s also means it’s my last chance to poke a hole in \cBride{\their} impeccable facade. I’d love nothing more than to catch \cBride{\them} doing something, anything wrong. Nobody’s allowed to be that perfect! Then, there’s \cAnarchist{\nickname}, one of the Assyrian peacemakers. I know \cAnarchist{\nickname} only as a mousy professor from that third-year seminar I took, so I’m curious to see what \cAnarchist{\they}’s like outside of class. Finally, there’s the ominous warning the Soulblades just sent out to everyone who’s ever studied with them-- their ancient assassin enemies, the anti-magic Blackguards, are apparently on the prowl once again. As a Soulblade, I’ve probably got a target painted on my back, but I can hope the Blackguards haven’t infiltrated the wedding, right? Right?

Fine, there may be a price on my head. I’ve brushed up on my acute poison remedies, and I’ll try to avoid getting caught alone in a remote location-- maybe I should stick to \cPoet{\nickname} as much as \cPoet{\they}’ll let me. Nonetheless, I intend to get my money and my signatures and get out of Scythia forever. To everyone who stands in my way-- screw you.


Note: Your birth parents’ names were Musa and Polutrupon. Polutrupon was a minor noble, descended directly from the Sabine royal family. Musa was a commoner, 
Note: You keep your royal title forever, even if you become Assyrian.
Note: Memnon, the father of the Scythian steward, was one of the most powerful Soulblade doctors ever.


\end{document}
